\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-19 submission/root.tex
Simulated inv axyb problem w.s.t. different scrambling rates

\section{A Brief Case Study With Completely Scrambled Data}
\label{sect5}

@@

Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$. Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), and we have:
\begin{IEEEeqnarray}{l}
M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
\\*
Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
\end{IEEEeqnarray}
Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently $Y$, Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use either Eq.~(\ref{equ15a}) or Eq.~(\ref{equ33a}) to get the optimal $\left( X_{k1}, Y_{k2} \right)$.

@@

In this paper, we developed a probabilistic approach to simultaneously obtain $X$ and $Y$ in the $AX=YB$ sensor calibration problem. Without a priori knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie groups is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates. Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean\textbf{-}group invariants, the correspondence is recovered to determine the correct solution among the eight candidates. In the numerical simulation, the method performs well with different sets of data samples. Future work will be to further develop the existing algorithm to solve for more general asynchronous cases, such as flipped data pairs or missing data in the data streams.

>>>>

\section{A Brief Case Study With Completely Scrambled Data}
\label{sect4}

@@

Given the equation $AX=YB$, apply an inverse on both sides of the equation and we will have $B^{-1}Y^{-1} = X^{-1}A^{-1}$. Following the same derivations from Eq.~(\ref{equ5}) to Eq.~(\ref{equ15b}), we have:
\begin{IEEEeqnarray}{l}
M_{B^{-1}} Y^{-1} = X^{-1} M_{A^{-1}} \IEEEyessubnumber\label{equ33a}
\\*
Ad(Y)\Sigma_{B^{-1}}Ad^{T}(Y) = \Sigma_{A^{-1}}. \IEEEyessubnumber\label{equ33b}
\end{IEEEeqnarray}
Similarly, Eq.~(\ref{equ33b}) can give eight candidates of $Y^{-1}$, or equivalently, the eight candidates of $Y$. Let $X_{k1}$ where $k1 = 1,2, \cdots, 8$ denote the $X$s obtained from Eq.(~\ref{equ15b}) and $Y_{k2}$ where $k2 = 1,2,\cdots, 8$ denote the $Y$s obtained from Eq.~(\ref{equ33b}), and we can use Eq.~(\ref{equ15a}) and Eq.~(\ref{equ33a}) to form a minimization problem as:
\begin{equation}
\underset{k1, k2}{min} ||M_A X_{k1} - Y_{k2} M_B ||_F + ||M_B^{-1} Y^{-1}_{k2} - X^{-1}_{k1} M_A^{-1} ||_F
\end{equation}
which can give the optimal $(X_{k1}, Y_{k2})$ pair. We call this approach the \textit{prob} method, and compare it with Li's method for testing its effectiveness of handling scrambled data sets. For simplicity, we use Eq.~(\ref{equ33a}) and Eq.~(\ref{equ33b}) to generate $\{B_i\}$, whereas compute $\{A_i\}$ using $A_i = X^{-1} Y B_i$ without exerting noise on $B_i$. Then $\{A_i\}$ is scrambled at each percentage from $0\%$ up to $100\%$. 50 times of simulations are performed for each percentage rate and the same error metrics are used as in Section \label{sect5}. As shown in Fig.~(\ref{fig7}) and Fig.~(\ref{fig8}), as the percentage of scrambled data goes up, the errors in rotation and translation for Li's method gradually diverge, while the errors for the $prob$ method are very stable and small. This shows the significant advantage of the probabilistic method in handling disordered data sets. However, Li's method is still more accurate when the exact correspondence is known between $\{A_i\}$ and $\{B_i\}$.

\begin{figure}[!t]
\centering
\includegraphics[width=3.2in]{Figure/fig7.eps}
\caption{Rotation error in X and Y v.s. scrambling rate for the $prob$ and Li's methods}
\label{fig7}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=3.2in]{Figure/fig8.eps}
\caption{Translation error in X and Y v.s. scrambling rate for the $prob$ and Li's methods}
\label{fig8}
\end{figure}

@@

In this paper, we developed a probabilistic approach to simultaneously obtain $X$ and $Y$ in the $AX=YB$ sensor calibration problem. Without a priori knowledge of the correspondence between $\{A_i\}$ and $\{B_j\}$, the proposed probabilistic method on Lie groups is used to constrain the possible solutions of $X$ and $Y$ to eight pairs of candidates. Given shifted data streams of $\{A_{i+s}\}$ and $\{B_i\}$, using the correlation theorem with Euclidean\textbf{-}group invariants, the correspondence is recovered to determine the correct solution among the eight candidates. In the numerical simulation, the method performs well with different sets of data samples. Lastly, we brought up a new approach to deal with completely disordered data sets and show its effectiveness in simulation. Future work will be to further develop the existing algorithm to solve for more general asynchronous cases, such as flipped data pairs or missing data in the data streams.
